### 2016-10-07 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
Edits

temp <- subset(dd,LayYear %in% c(2000:2008))

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL,col=factor(LayYear)))+
  ylab('RTL') + 
  xlab('Age (months)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  stat_smooth(method = 'lm',formula = y~log(x),se=F)
  annotate('text',x = 1,y = 2.9,label = 'A')

temp <- subset(dd,DeltaAge !=0)

Fig1B <- ggplot(temp,aes(x = DeltaAge,y = RTL))+
  ylab('RTL') + 
  xlab(expression(Delta*' age (months)')) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_point(col='grey')+
  stat_smooth(method = 'lm',col = 'darkblue',fill = 'darkblue')+
  annotate('text',x = -100,y = 2.9,label = 'B')

pdf('Figures/Figure 1.pdf',
    width = 4,
    height = 8,
    paper = 'a4')
multiplot(Fig1A,Fig1B,layout=matrix(c(1,2),nrow = 2,byrow=T))
dev.off()

@@

#Run the model
lm2 <- lmer(RTL ~  LogAge+Tarsus + Helper + NonHelper + Sex + BodyMass  +yday + Insect + Density + (1|LayYear) + (1|BirdID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

@@

```{r Figure 4}

temp <- dd3
temp[,'Age (months)'] <- factor(temp$Agemonths)

Fig4A <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab('Adult RTL') + 
  xlab('juvenile RTL') +
    xlim(c(0,3))+
  ylim(c(0,3))+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  geom_abline(slope = 1,intercept = 0,lty = 2)+
  geom_point()+
  scale_colour_manual(values = c('navy','red'))+
  annotate('text',x = 0,y = 3,label = 'A')

mycols <- topo.colors(length(keep2))

Fig4B <- ggplot(temp,aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
  geom_point(alpha = 1,col='grey')+
geom_line(col = 'darkgrey',alpha = 0.2)+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  #scale_colour_brewer(palette = 'Set1')+
  annotate('text',x = 0,y = 3,label = 'B')

Fig4C <- ggplot(ddL,aes(col=Group,fill = Group,y = ..scaled..,x = DeltaRTL))+
    geom_density(alpha = 0.2)+
  theme_classic()+
  ylab ('Scaled density')+
  xlab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none',
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2)+
  annotate('text',x = -2,y = 1,label = 'C')

Fig4D <- ggplot(temp,aes(col=factor(DeltaRTLF),y = DeltaRTL,x = TimeDiff))+
    geom_point()+
  theme_classic()+ 
  xlab ('Follow up time (years)')+
  ylab(expression(Delta*'RTL'))+
  ylim(c(-2,2))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('navy','red'))+
    geom_abline(slope = 0,intercept = 0,lty = 2)+
  annotate('text',x = 0,y = 2,label = 'D')

pdf('Figures/Figure 4.pdf',
    width = 8,
    height = 7,
    paper = 'a4')
multiplot(Fig4A,Fig4B,Fig4C,Fig4D,layout=matrix(c(1,2,3,4),nrow=2,byrow=T))
dev.off()

@@

anova(m2,m3,m4,m5)
summary(m2)
summary(m3)

>>>>

Fig1A <- ggplot(temp,aes(x = Agemonths,y = RTL,group = BirdID,col=factor(BirdID)))+
  geom_point(alpha = 1,col='grey')+
geom_line(col = 'darkgrey',alpha = 0.2)+
  xlab('Age (years)') +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'none')+
  geom_smooth(col = 'black',fill = 'black',lwd = 0.5,aes(group = NULL),method = 'lm',formula = y~log(x))+
  annotate('text',x = 0,y = 3,label = 'A')

Fig1B <- ggplot(temp,
       aes(x = RTL,
           y = RTL1)) +
  ylab('Adult RTL') + 
  xlab('juvenile RTL') +
    xlim(c(0,3))+
  ylim(c(0,3))+
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_text(size = 12),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_point(col = 'grey')+
  geom_abline(slope = 1,intercept = 0,lty = 2)+
  annotate('text',x = 0,y = 3,label = 'B')

Fig1C <- ggplot(ddL,aes(col=Group,fill = Group,y = ..scaled..,x = DeltaRTL))+
    geom_density(alpha = 0.2)+
  theme_classic()+
  ylab ('Scaled density')+
  xlab(expression(Delta*'RTL'))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = 'none',
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
  scale_colour_manual(values = c('darkgrey','gold'))+
  scale_fill_manual(values = c('darkgrey','gold'))+
  geom_vline(xintercept = 0,lty = 2)+
  annotate('text',x = -2,y = 1,label = 'C')

Fig1D <- ggplot(temp,aes(y = DeltaRTL,x = TimeDiff))+
    geom_point(col = 'grey')+
  theme_classic()+ 
  xlab ('Follow up time (years)')+
  ylab(expression(Delta*'RTL'))+
  ylim(c(-2,2))+
    theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
        legend.position = c('none'),
        legend.title = element_blank(),
        axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black')) +
    geom_abline(slope = 0,intercept = 0,lty = 2)+
  annotate('text',x = 0,y = 2,label = 'D')

pdf('Figures/Figure 1.pdf',
    width = 8,
    height = 7,
    paper = 'a4')
multiplot(Fig1A,Fig1B,Fig1C,Fig1D,layout=matrix(c(1,2,3,4),nrow=2,byrow=T))
dev.off()

@@

#Run the model
lm2 <- lmer(RTL ~  LogAge+Tarsus + Helper + NonHelper + Sex + BodyMass  +yday + Insect + Density + (1|LayYear) + (1|BirdID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)

@@

@@

m1 <- lmer(RTL~(Agemonths)+(1|BirdID)+(1|LayYear),data=dd)
m2 <- lmer(RTL~Ageclass+(1|BirdID)+(1|LayYear),data=dd)
m3 <- lmer(RTL~LogAge+(1|BirdID)+(1|LayYear),data=dd)

anova(m1,m2,m3)
summary(m2)
summary(m3)

dd3$LogAge <- log(dd3$Agemonths)
m1 <- lmer(RTL1~RTL+(1|LayYear),data=dd3)
summary(m1)
